---
title: "QR Codes"
format: html
eval: FALSE
---


This page was used to generate the QR codes needed for our Cyto 2026 poster using the `qrcode` R package. 

```{r}
library(qrcode)
```


# Helper Function

```{r}
QR_Helper <- function(url, output, filename){

code <- qr_code(url)

TheFileName  <- paste0(filename, ".svg")

StoreHere <- file.path(output, TheFileName)

generate_svg(code, filename = StoreHere)
#plot(code)
}
```


# Bioconductor Zulip

```{r}

QR_Helper(url="https://community-bioc.zulipchat.com/join/4k2tpsy7h6zjbaduydwm2n56/",
    output="outputs", 
    filename="BioconductorZulip")
```
# Homepage

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/",
    output="outputs", 
    filename="Homepage")
```

# Schedule

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html",
    output="outputs", 
    filename="Schedule")
```

# UsingGitHub

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/00_GitHub/",
    output="outputs", 
    filename="UsingGithub")
```

# Installing R Packages

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/01_InstallingRPackages/",
    output="outputs", 
    filename="InstallingRPackages")
```

# FilePaths

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/02_FilePaths/",
    output="outputs", 
    filename="FilePaths")
```

# InsideFCSFile

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/03_InsideFCSFile/",
    output="outputs", 
    filename="InsideFCSFile")
```

# IntroTidyverse

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/04_IntroToTidyverse/",
    output="outputs", 
    filename="IntroTidyverse")
```

# GatingSets

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/05_GatingSets/",
    output="outputs", 
    filename="GatingSets")
```

# Visualizing_ggplot2

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/06_Visualizing/",
    output="outputs", 
    filename="Visualizing_ggplot2")
```

# Transformations

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/07_Transformations/",
    output="outputs", 
    filename="Transformations")
```

# WaysToGate

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/08_WaysToGate/",
    output="outputs", 
    filename="WaysToGate")
```

# RainingFunctions

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/09_Functions/",
    output="outputs", 
    filename="RainingFunctions")
```

# Downsampling

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/10_Downsampling/",
    output="outputs", 
    filename="Downsampling")
```

# DataForStats

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/11_DataForStats/",
    output="outputs", 
    filename="DataForStats")
```

# Yet to Be completed

# Spectral Signatures

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#spectral-signatures",
    output="outputs", 
    filename="SpectralSignatures")
```

# Similarities and Hotspots

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#similarities-and-hotspots",
    output="outputs", 
    filename="SimilaritiesHotspots")
```

# Unmixing

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#unmixing-in-r",
    output="outputs", 
    filename="Unmixing")
```

# Cleaning

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#cleaning-algorithms",
    output="outputs", 
    filename="Cleaning")
```

# Clustering

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#clustering-algorithms",
    output="outputs", 
    filename="Clustering")
```

# Normalizing

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#normalization-batch-effect-or-real-biology",
    output="outputs", 
    filename="Normalizing")
```

# Dimensionality

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#dimensionality-visualization",
    output="outputs", 
    filename="Dimensionality")
```

# Annotation

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#annotating-unsupervised-clusters",
    output="outputs", 
    filename="Annotation")
```

# GitHub

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#the-art-of-github-diving",
    output="outputs", 
    filename="GitHubDiving")
```

# XML

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#xml-files-all-the-way-down",
    output="outputs", 
    filename="XMLAllWayDown")
```

# Bioconductor

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#utilizing-bioconductor-packages",
    output="outputs", 
    filename="Bioconductor")
```

# First R Package

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#building-your-first-r-package",
    output="outputs", 
    filename="FirstRPackage")
```

# Quarto Website

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#everyone-gets-a-quarto-website",
    output="outputs", 
    filename="QuartoWebsite")
```

# Reproducibility

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#reproducibility-and-replicability",
    output="outputs", 
    filename="Reproducibility")
```

# OpenSoureLicense

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#open-source-licenses",
    output="outputs", 
    filename="OpenSourceLicenses")
```

# Validating

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#validating-algorthmic-tools",
    output="outputs", 
    filename="Validating")
```

# Databases

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#databases-and-repositories",
    output="outputs", 
    filename="Databases")
```

# Assembling Web

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#assembling-web-data",
    output="outputs", 
    filename="AssemblingWeb")
```

# Future

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Schedule.html#future-directions",
    output="outputs", 
    filename="Future")
```

# Survey Link

```{r}
QR_Helper(url="https://docs.google.com/forms/d/e/1FAIpQLScfh8ibMF3ldyM2W2jGZGX09j2fYcI3isiboKWi3UQ31b9OdQ/viewform?usp=publish-editor",
    output="outputs", 
    filename="Survey2")

```

# YouTube

```{r}
QR_Helper(url="https://www.youtube.com/@CytometryInR",
    output="outputs", 
    filename="YouTube")

```

# Discussions

```{r}
QR_Helper(url="https://github.com/UMGCCCFCSR/CytometryInR/discussions",
    output="outputs", 
    filename="Discussions")

```


# GitHub

```{r}
QR_Helper(url="https://github.com/UMGCCCFCSR/CytometryInR",
    output="outputs", 
    filename="GitHub")

```


# Homeworks

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Homeworks.html",
    output="outputs", 
    filename="Homeworks")

```



# FlowCore

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/course/03_InsideFCSFile/#flowcore",
    output="outputs", 
    filename="flowCore")

```

# Defense

```{r}
QR_Helper(url="https://www.youtube.com/live/K7iae7IWS24?si=lKUIVsOkYWC6Rurn",
    output="outputs", 
    filename="Defense")

```

# Announcements

```{r}
QR_Helper(url="https://umgcccfcsr.github.io/CytometryInR/Announcements.html",
    output="outputs", 
    filename="Announcements")

```

# AGPL3

```{r}
QR_Helper(url="https://www.gnu.org/licenses/agpl-3.0.en.html",
    output="outputs", 
    filename="AGPL3")

```


# CC-BY-SA

```{r}
QR_Helper(url="https://creativecommons.org/licenses/by-sa/4.0/",
    output="outputs", 
    filename="CCBYSA")
https://discord.gg/ZmyPYUQr9Q
```

# Discord

```{r}
QR_Helper(url="https://discord.gg/ZmyPYUQr9Q",
    output="outputs", 
    filename="Discord")

```






































